---
title: "Shiny Project"
output: html_document
---

### Loading libraries
```{r, message=FALSE, error=FALSE, warning=FALSE}
library(riingo)
library(tidyquant)
library(PerformanceAnalytics)
library(highcharter)
library(shiny)
library(lubridate)
library(tidyverse)
library(shinythemes)
library(tibbletime)
```

* **Riingo is the package build to interact with the Tiingo API, to pull daily crypto data.**
* **PerformanceAnalytics, highcharter and tidyquant are packages specifically towards Financial data analysis. Tidy quant package is developed employing tidy princples **

### Scraping data from Tiingo API
```{r, message=FALSE, error=FALSE, warning=FALSE}
tiingo_api_key('eaff4a7b5ef40d77fe14a1538b429246e728e062')
tickers = supported_tickers(type = "crypto")

coins = c("btcusd","dogeusd","ethusd","xrpusd","ltcusd")
chk = tq_get(coins,get = "tiingo.crypto",from = "2018-01-01",to = "2021-04-20",resample_frequency = "1day")
table(chk$symbol)

prices = chk
prices$date = ymd(prices$date)
```

* **Tickers table gives a list of all the cryto currencies supported by Tiingo API, in addition to crypto data, Tiingo is also used to pull in data for stocks and other financial instruments** 

```{r, message=FALSE, error=FALSE, warning=FALSE}
ui = fluidPage(theme=shinytheme("darkly"),
               
               titlePanel("Crypto Currency Strategy Analysis Dashboard"),
               
               sidebarLayout(
                 
                 sidebarPanel(numericInput(inputId = "invest", label ="Investment", value = 1000),
                              dateRangeInput(inputId = "date", label = "Time Range", 
                                             start = "2019-01-01", end ="2021-04-20", 
                                             min = "2019-01-01", max ="2021-04-20",
                                             format = "yyyy-mm-dd"),
                              selectInput("coin", label = "Select Crypto", choices = list("Bitcoin" = "btcusd", "Doge coin" = "dogeusd", "Ethereum" = "ethusd","Ripple"="xrpusd","Lite Coin"="ltcusd"), selected = "btcusd"),
                              selectInput("week", label = "Select DA freq(week(s))", choices = list("Weekly" = 1, "Bi Weekly" = 2, "Once in 3 Weeks" = 3,"Once in 4 Weeks" = 4), selected = 1)
                 ), 
                 
                 mainPanel(highchartOutput("trend"),highchartOutput("profit")
                 )
               )
)
```

* **Themes can be applied to shiny dashboards through shinythemes package**
* **Followed a side panel, main panel layout for the UI**
* **Dashboard takes in 4 inputs, and produces 2 outputs**
* **The min and max dates can be specified on the input date ranges**
* **The motivation is to create interactive plots. The package highcharter in pulling Javascript styled into R. To render these graphs, highchartOutput is used instead of the standard plotOutput**
* ****


```{r, message=FALSE, error=FALSE, warning=FALSE}

# As in the case with the Plothighchart, renderHighchart is also used specifically to render interactive charts onto Shiny dashboard
server <- function(input, output, session) {
  
  output$trend =   renderHighchart({
    
    prices = chk %>% filter(date>=input$date[1]&date<=input$date[2]&symbol==input$coin)
# DA is a strategy wherein equal investments are made in a timely manner, once in a week, 2 weeks.. instead of decreasing the volatility (variance) of the investment
    
# All the 3 inputs go into the below 3 variables 
    invest = input$invest
    freq = as.numeric(input$week)
    denom = 400
# Strategy 1 - Dollar Averaging
# Below we are creating a money invested column. It is tricky with the mutate function. Instead iterated over a vector with the custom rules to come up with the money invested column
    vec=c()
    dum =input$invest
    i = 1
    while(dum != 0){
      if(dum>denom){
        vec = c(vec,rep(denom*i,freq*7))
        dum = dum-denom
        i =i+1
      }
      else{
        vec = c(vec, rep(invest,(nrow(prices)-length(vec))))
        dum =0
      }
    }
    
    
    prices$money_inv_da = vec
    prices = as.data.frame(prices)
    
    
    coin_vec =c()
    i =1
    for (i in seq(nrow(prices))){
      if(i==1){
        coin_vec = c(coin_vec,prices$money_inv_da[1]/prices$open[1])
      }
      else if(prices$money_inv_da[i]==prices$money_inv_da[i-1]){
        coin_vec = c(coin_vec,coin_vec[i-1])
      }else{
        coin_vec = c(coin_vec,(prices$money_inv_da[i]-prices$money_inv_da[i-1])/prices$open[i] + coin_vec[i-1])
      }
      
    }
    
    prices$coin_inv_da = coin_vec
    
    prices$portfolio_da = prices$coin_inv_da*prices$open
    
#Strategy 2 - Golden cross, death cross method 
#Whenever 50 day (shorter trend) MA goes over the 200 day (longer trend) MA , it is a signal for bullish market and is a signal to buy and viceversa is a signal for a bullish trend and sell 
    
    roll_mean_50 = rollify(mean,window = 50)
    roll_mean_200 = rollify(mean,window = 200)
#Rollify is a function which creates functions across the number of rows specified in the window
        
    prices_ma = chk%>% mutate(ma_50 = roll_mean_50(open), ma_200 = roll_mean_200(open)) %>% 
      mutate("signal" = ifelse(ma_50>ma_200,1,0)) %>% 
      filter(date>=input$date[1]&date<=input$date[2]&symbol==input$coin)
# Creating a signal     
    
    money_poc_ma =c()
    money_inv_ma =c()
    coin_inv_ma =c()

# Money in pocket column is a important column in computing this algorithm
# There can be 3 use cases in total, buy, sell and continue with the either once 
    i=1
    
    for (i in seq(nrow(prices_ma))){
      if(i==1){
        if (prices_ma$signal[1]==0){
          money_poc_ma[1] = invest
          money_inv_ma[1] = 0
          coin_inv_ma[1]=0
        }else{
          money_poc_ma[1] = 0
          money_inv_ma[1] = invest
          coin_inv_ma[1]=invest/prices_ma$open[1]}
      }else{
        if(prices_ma$signal[i]==prices_ma$signal[i-1]){
          money_poc_ma[i] = money_poc_ma[i-1] 
          money_inv_ma[i] = money_inv_ma[i-1]
          coin_inv_ma[i] = coin_inv_ma[i-1]
        }else if(prices_ma$signal[i]==0&prices_ma$signal[i-1]==1){
          money_poc_ma[i] = coin_inv_ma[i-1]*prices_ma$open[i]
          money_inv_ma[i] = 0
          coin_inv_ma[i]=0
        }else if(prices_ma$signal[i]==1&prices_ma$signal[i-1]==0){
          money_poc_ma[i] = 0
          money_inv_ma[i] = money_poc_ma[i-1]
          coin_inv_ma[i]=money_poc_ma[i-1]/prices_ma$open[i]
        }
      }
    }
    
    prices_ma$money_poc_ma = money_poc_ma
    prices_ma$money_inv_ma =money_inv_ma
    prices_ma$coin_inv_ma =coin_inv_ma
    
    # Portfolio amount at any time is equal to the money in pocket + money in investment 
    prices_ma$portfolio_ma = prices_ma$money_poc_ma+prices_ma$coin_inv_ma*prices_ma$open
    
    prices$portfolio_ma = prices_ma$portfolio_ma
    
    prices_pivot = prices %>% select(date,portfolio_da, portfolio_ma) %>%  pivot_longer(cols = 2:3,names_to = "Strategy")
    prices_pivot$Strategy[prices_pivot$Strategy=="portfolio_da"] ="Dollar Averaging"
    prices_pivot$Strategy[prices_pivot$Strategy=="portfolio_ma"] ="Golden Cross/ Death Cross"
    
    hchart(prices_pivot,hcaes(x=ymd(date),y=round(value,1), group ="Strategy"), type ="line") %>% hc_exporting(enabled =TRUE) %>% 
      hc_tooltip(crosshairs = TRUE, backgroundColor = "#FCFFC5",shared = TRUE, borderWidth = 2) %>%
      hc_title(text="Portfolio value graph",align="center") %>%
      hc_subtitle(text="Data Source: Tingo API",align="right") %>%
      hc_add_theme(hc_theme_elementary()) %>% 
      hc_xAxis(title = list(text = "Date")) %>% 
      hc_yAxis(title = list(text = "Portfolio Value"))}
  )
  output$profit =   renderHighchart({
    
    prices = chk %>% filter(date>=input$date[1]&date<=input$date[2]&symbol==input$coin)
    
    invest = input$invest
    freq = as.numeric(input$week)
    denom = 400
    
    vec=c()
    dum =input$invest
    i = 1
    while(dum != 0){
      if(dum>denom){
        vec = c(vec,rep(denom*i,freq*7))
        dum = dum-denom
        i =i+1
      }
      else{
        vec = c(vec, rep(invest,(nrow(prices)-length(vec))))
        dum =0
      }
    }
    
    
    prices$money_inv_da = vec
    prices = as.data.frame(prices)
    
    
    coin_vec =c()
    i =1
    for (i in seq(nrow(prices))){
      if(i==1){
        coin_vec = c(coin_vec,prices$money_inv_da[1]/prices$open[1])
      }
      else if(prices$money_inv_da[i]==prices$money_inv_da[i-1]){
        coin_vec = c(coin_vec,coin_vec[i-1])
      }else{
        coin_vec = c(coin_vec,(prices$money_inv_da[i]-prices$money_inv_da[i-1])/prices$open[i] + coin_vec[i-1])
      }
      
    }
    
    prices$coin_inv_da = coin_vec
    
    prices$portfolio_da = prices$coin_inv_da*prices$open
    
    ### Golden cross, death cross method 
    
    roll_mean_50 = rollify(mean,window = 50)
    roll_mean_200 = rollify(mean,window = 200)
    
    prices_ma = chk%>% mutate(ma_50 = roll_mean_50(open), ma_200 = roll_mean_200(open)) %>% 
      mutate("signal" = ifelse(ma_50>ma_200,1,0)) %>% 
      filter(date>=input$date[1]&date<=input$date[2]&symbol==input$coin)
    
    money_poc_ma =c()
    money_inv_ma =c()
    coin_inv_ma =c()
    
    i=1
    
    for (i in seq(nrow(prices_ma))){
      if(i==1){
        if (prices_ma$signal[1]==0){
          money_poc_ma[1] = invest
          money_inv_ma[1] = 0
          coin_inv_ma[1]=0
        }else{
          money_poc_ma[1] = 0
          money_inv_ma[1] = invest
          coin_inv_ma[1]=invest/prices_ma$open[1]}
      }else{
        if(prices_ma$signal[i]==prices_ma$signal[i-1]){
          money_poc_ma[i] = money_poc_ma[i-1] 
          money_inv_ma[i] = money_inv_ma[i-1]
          coin_inv_ma[i] = coin_inv_ma[i-1]
        }else if(prices_ma$signal[i]==0&prices_ma$signal[i-1]==1){
          money_poc_ma[i] = coin_inv_ma[i-1]*prices_ma$open[i]
          money_inv_ma[i] = 0
          coin_inv_ma[i]=0
        }else if(prices_ma$signal[i]==1&prices_ma$signal[i-1]==0){
          money_poc_ma[i] = 0
          money_inv_ma[i] = money_poc_ma[i-1]
          coin_inv_ma[i]=money_poc_ma[i-1]/prices_ma$open[i]
        }
      }
    }
    
    prices_ma$money_poc_ma = money_poc_ma
    prices_ma$money_inv_ma =money_inv_ma
    prices_ma$coin_inv_ma =coin_inv_ma
    
    prices_ma$portfolio_ma = prices_ma$money_poc_ma+prices_ma$coin_inv_ma*prices_ma$open
    
    prices$portfolio_ma = prices_ma$portfolio_ma
    prices = prices %>% mutate("profit_da"= prices$portfolio_da-prices$money_inv_da,"profit_ma"=portfolio_ma-input$invest) %>% 
      select(date,profit_da,profit_ma)
    
    prices_pivot = prices %>% select(date,profit_da, profit_ma) %>%  pivot_longer(cols = 2:3,names_to = "Strategy")
    prices_pivot$Strategy[prices_pivot$Strategy=="profit_da"] ="Dollar Averaging"
    prices_pivot$Strategy[prices_pivot$Strategy=="profit_ma"] ="Golden Cross/ Death Cross"
    
    hchart(prices_pivot,hcaes(x=ymd(date),y=round(value,1), group ="Strategy"), type ="line") %>% hc_exporting(enabled =TRUE) %>% 
      hc_tooltip(crosshairs = TRUE, backgroundColor = "#FCFFC5",shared = TRUE, borderWidth = 2) %>%
      hc_title(text="Net profit/loss graph",align="center") %>%
      hc_subtitle(text="Data Source: Tingo API",align="right") %>%
      hc_add_theme(hc_theme_elementary()) %>% 
      hc_xAxis(title = list(text = "Date")) %>% 
      hc_yAxis(title = list(text = "Net gains"))})  
}

```

```{r, message=FALSE, error=FALSE, warning=FALSE}
shinyApp(ui = ui, server = server)
```
